\clearpage
\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{25}
 \bibitem{armstrong00}
 Armstrong, M.A. 
 \emph{Basic Topology.} 
 England:
 Editorial Board, 2000.
 
 \bibitem{coxeter}
 Coxeter, H.S.M.
 \emph{Introduction to Geometry.} 
 Toronto:
 John Wiley and Sons Inc, 1969.

 \bibitem{chronister}
 Chronister, James.
 \emph{Blender Basics.} 
 Estados Unidos:
 2004.

 \bibitem{engelking89}
 Engelking, Ryszard.
 \emph{General Topology.}
 Berlin:
 Hildermann, 1989.

 \bibitem{engelking92}
 Engelking, Ryszard y Karol Sieklucki.
 \emph{Topology: A Geometric Approach.}
 Berlin: Hildermann, 1992. 

 \bibitem{hatcher}
 Hatcher, Allen.
 \emph{Algebraic Topology.}
 Cambridge:
 Cambridge University Press, 2002.

 \bibitem{hoffman}
 Hoffman, Kenneth y Ray Kunze.
 \emph{Linear Algebra, second edition.}
 New Jersey:
 Prentice Hall. Inc, 1961. 

 \bibitem{kackzynski}
 Kackzynski, T., K. Mischainkow y M. Mrozen.
 \emph{Algebraic Topology: A Computational Approach.}
 2000.

 \bibitem{kosniowski}
 Kosniowski, Czes.
 \emph{Topología Algebraica.}
 Barcelona:
 Editorial Revert, 1986.

 \bibitem{lefschetz}
 Lefschetz, Solomon.
 \emph{Algebraic Topology.}
 Rhode Island:
 American Mathematical Society, 1991.

 \bibitem{may}
 May, J. P.
 \emph{A Concise Course in Algebraic Topology.}
 Chicago.

 \bibitem{mill}
 Mill, J. Van.
 \emph{Infinite-Dimensional Topology.}
 Amsterdam:
 Elsevier Science Publications B. V, 1989.

 \bibitem{munkres}
 Munkres, James R.
 \emph{Topology.}
 New York:
 Prentice Hall Inc, 2000.

 \bibitem{roseman}
 Roseman, Dennis.
 \emph{Elementary Topology.}
 New Jersey:
 Prentice Hall Inc, 1999.

 \bibitem{sato}
 Sato, Hajime.
 \emph{Algebraic Topology: An Intuituve Approach.}
 Rhode Island:
 American Mathematical Society, 1996.

 \bibitem{zomorodian}
 Zomorodian, Afra J.
 \emph{Topology for Computing.}
 United States:
 Cambridge University Press, 2005.
\end{thebibliography}

\bibliography{tesis}